R for Clinical Study Reports and Submission

### 2021-09-15 index.Rmd
add bookdown

```{r, include = FALSE}
library(bslib)
library(xml2)
library(downlit)
library(haven) 
library(dplyr) 
library(tidyr) 
library(r2rtf) 
library(knitr)
library(kableExtra)
```

>>>>

```{r, include = FALSE}
library(bslib)
library(xml2)
library(downlit)
library(haven) 
library(dplyr) 
library(tidyr) 
library(r2rtf) 
library(knitr)
library(kableExtra)
library(bookdown)
```
